---
title: "Data_summary_land"
output: html_document
---

```{r}
library(foreign)
library(dplyr)
land <- read.dbf("C:/Users/akell/Desktop/Spring_2018/Research/GIS/land_locations.dbf")
ows <- subset(land, land$month > 6 & land$month < 11)
```

#all land

print(paste("There are 83 unique individuals recorded using land (all months, all years)"))
unique((land$year))
```

If all months are included, we have "land" data for all years 2004-2016

```{r}
unique(ows$animal)
print(paste("There are 83 unique individuals in the 'ows' subset (months 7-10)"))
unique(ows$year)
```
Open Water Season (OWS): Years absent=2007, 2010, 2016

```{r}
print(paste("All Land Points by Animal"))
table(land$animal, land$year)
```
```{r}
print(paste("OWS Land Points by Animal"))
table(ows$animal, ows$year)
```

```{r}
print(paste("Number of fixes, land v. OWS"))
nrow(land)
nrow(ows)
```
```{r}
#Test for duplicated data
tt<-paste(land$animal, land$datetime)
table(duplicated(tt, fromLast=F)) #Test if you have duplicated data
print(paste("No data points are duplicated"))
```

```{r}
library(adehabitatLT)
library(lubridate)
library(dplyr)

traj.pb<-as.ltraj(xy=ows[,c("X","Y")], date=ows$datetime, id=as.character(ows$animal))
summary(traj.pb)



```

```{r}
# Graph Speed before cleaning data
hist(traj.pb2$dist,xlab="Speed",main="Speed distribution - PB")
plot(traj.pb2$dist,type="p",xlab="Index",ylab="Speed",main="Overall Speed distribution - PB",cex=.5)
```

