---
title: "May 2018"
author: "Annie Kellner"
date: "May 8, 2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
rm(list = ls())
land <- read.csv("Land.csv")
```
#All land

83 unique individuals use land from 2004-2016. If all months are included (not just open water season), all years are represented.  

Number of data points per animal, per year (all months included):

```{r echo=FALSE} 
table(land$animal, land$year)
```

#Open Water Season, defined as July - October
Years without data: 2007, 2010, 2016

```{r echo=FALSE}
ows <- subset(land, land$month > 6 & land$month < 11)
table(ows$animal, ows$year)
```

Questions:   
* How little data is too little? e.g., 14 points? 15 points? Should these be deleted or included?  
* Should I divide by year for easier analysis?

Total number data points 'all land'| Total number data points 'OWS'
-----------------------------------|------------------------------
`r nrow(land)`                     | `r nrow(ows)`  

```{r echo=FALSE}
library(adehabitatLT)
library(lubridate)
library(knitr)
library(kableExtra)

ows <- subset(land, land$month > 6 & land$month < 11)
ows$datetime <- ymd_hms(paste(ows$year, ows$month, ows$day, ows$hour, ows$minute, ows$second, sep = "-"), tz="US/Alaska") #use lubridate fxn to format datetime, add column to land dataframe


traj.pb<-as.ltraj(xy=ows[,c("X","Y")], date=ows$datetime, id=as.character(ows$animal))
Summary.traj.pb <- summary(traj.pb)
Summary.traj.pb$DaysTrack <-round(difftime(Summary.traj.pb$date.end,Summary.traj.pb$date.begin, units="days"),digits=1)
Summary.traj.pb$Records <- Summary.traj.pb$nb.reloc-Summary.traj.pb$NAs
Summary.traj.pb$PctComplete <- round((Summary.traj.pb$nb.reloc-Summary.traj.pb$NAs)/Summary.traj.pb$nb.reloc*100,digits=1)

#Make table prettier
Summary.traj.pb %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
Next steps:  
  * See how well date.begin dates match up with first land point (test some %?)  
    + Atwood 2016: earliest date July 22, 2000; latest Aug 6, 1993  
                   earliest departure Aug 14, 1993; latest departure Nov. 7, 2013  
  * Identify first land points  
  * Can see 2013 bears are still on land October 31 --> extend the season for this year  
  * Check into other years: 2006, 2008, 2012, 2013, 2014 (some late stays might reflect         denning --> would not count)

  
```{r echo=FALSE}
traj.pb2<-ld(traj.pb)
summary(traj.pb2$dist)
```
  
  *Need to place missing values in trajectories  
    + Do this by year? Need to read more about this.
  
```{r echo=FALSE}
hist(traj.pb2$dist,xlab="Speed",main="Speed distribution - PB")
```
```{r}
plot(traj.pb2$dist,type="p",xlab="Index",ylab="Speed",main="Overall Speed distribution - PB",cex=.5)
```
* default = m?  
* Looked into two outliers --> definitely not correct  
* Need to look into biologically plausible distances for PB. Also take into account variability in interval between fixes.





















